Developing a preprint culture in biology

### 2012-10-11 ms.tex

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free, with a onetime
(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited
public preprints. The preprint server is not tied to the journal, so preprints
can be posted regardless of where they will eventually be submitted for
publication.

@@

One of drawback of making publication easier is the proliferation of studies of
uneven quality. A trade-off between the intensity of the peer-review filtering
and the benefits to science has been hypothesized \cite{Aarssen2012}.  With
increasingly stringent peer reviewing, the quality of published papers and
easiness of finding discoveries might increase, at the cost of censorship, an
increased load on authors and reviewers, and more delays for publication.
Preprints are simply bypassing this model for what we believe is the progress of
science: they speed up the dissemination of scientific discoveries, impede
censorship and put on reader's shoulders the responsibility to judge originality
and pertinence.

>>>>

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free, with a onetime
(\emph{i.e.} lifetime) fee of 99 dollars required to allow an author to post unlimited
public preprints. The preprint server is not tied to the journal, so preprints
can be posted regardless of where they will eventually be submitted for
publication.

@@

One of drawback of making publication easier is the proliferation of studies of
uneven quality. A trade-off between the intensity of the peer-review filtering
and the benefits to science has been hypothesized \cite{Aarssen2012}.  With
increasingly stringent peer reviewing, the quality of published papers and
easiness of finding discoveries might increase, at the cost of censorship, an
increased load on authors and reviewers, and greater delays for publication.
Preprints are simply bypassing this model for what we believe is the progress of
science: they speed up the dissemination of scientific discoveries, impede
censorship and put on reader's shoulders the responsibility to judge originality
and pertinence.
